---
title: "Plotting/analyses of ØKOKYST FerryBox"
author: "Helene Frigstad"
date: "15 feb 2022"
output: html_notebook

---

## 0. Libraries
```{r}
library(dplyr)
library(purrr)
library(ggplot2)
library(lubridate)
library(readxl)
library(tidyr)
library(RColorBrewer)
library(patchwork) # for arranging plots in panels
# RColorBrewer::display.brewer.all()
```


## 1. Read and clean files
### a. read
* this file is produced in script "Read_and_check_OKOKYST_Klima.Rmd"
```{r}

dir("Datasett")

df <- read.delim ("Datasett/OKOKYST_Klima_cleaned.txt")
df2 <- read.delim ("Datasett/OKOKYST_Klima_cleaned_merged.txt")

#units
#DOC	Fluorescens	KlfA	NH4-N	Nitrogen part	NO3+NO2-N	O2	O2	O2 (metning)	PO4-P	POC	P-PO4	Salinitet	SGR - Suspendert gløderest	Siktdyp	SiO2	STS	Temperatur	Tetthetsanomali	TOTN	TOTP	TOTP_P	TSM	Turbiditet
#mg/L C	µg/l	µg/l	µg/l	µg/l N	µg/l	mg/L	ml/l	%	µg/l	µg/l C	µg/l P		mg/l	m	mg/l	mg/l	C	kg/m3	µg/l	µg/l	µg/l P	mg/l	FNU
df<-df2
# convert back to Date
df$Date <- as.Date(df$Date)

str(df)

# station naming
df$StationId <- as.factor (df$StationId)
#order stations from along coastline for ggplot

df$StationId <- factor(df$StationId, levels = c("VT3", "VT16", "VT71", "VR54", "VR58", "VR21"))

## Add months as nr and names
df<- df  %>% mutate(Month=Date, Month_txt=Date)
df$Month<- strftime(df$Month,"%m")
df$Month_txt<- strftime(df$Month_txt,"%B")

```
$MonthPlots

### a. Set common options for ggplot
```{r}
theme_set(theme_minimal())

# Set date axis limits c(min, max)
# range (df1$Date)
# min <- as.Date("2017-12-01")
# max <- as.Date("2020-11-30")
#p + scale_x_date(limits = c(min, max))


str (df)
```


### b. Timeseries pr station
```{r}
str(df)

#DOC timeser with COVID shutdown of Trollfjord
df %>%
  ggplot(aes(Date, DOC)) + 
    geom_point() + geom_smooth() +
      labs(title = "", x = "", y = "DOC (mg/L)") +
      geom_vline(xintercept = as.numeric(ymd("2020-03-14")), linetype="dashed", 
                color = "red", size=1) +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

#ggsave ("Figures/OKOKYST_Klima/DOC_allstations.png", width = 8, height = 6, dpi=500)

df %>%
  filter(StationCode == "VT3" | StationCode == "VT71" | StationCode == "VR54") %>%
  ggplot(aes(Date, DOC)) + 
    geom_point() + geom_smooth() +
      labs(title = "", x = "", y = "DOC (mg/L)") +
      geom_vline(xintercept = as.numeric(ymd("2020-03-14")), linetype="dashed", 
                color = "red", size=1) +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/OKOKYST_Klima/DOC_allstations.png", width = 8, height = 6, dpi=500)

df %>%
  ggplot(aes(Date, DOC)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationId, ncol=2) +
      labs(title = "", x = "", y = "DOC (mg/L)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/OKOKYST_Klima/DOC_pr_station.png", width = 8, height = 6, dpi=500)

df %>%
  ggplot(aes(Date, TSM)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationId, ncol=2) +
      labs(title = "", x = "", y = "TSM (mg/L)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/OKOKYST_Klima/TSM_pr_station.png", width = 8, height = 6, dpi=500)

df %>%
  ggplot(aes(Date, POC)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationId, ncol=2) +
      labs(title = "", x = "", y = "POC ") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/OKOKYST_Klima/POC_pr_station.png", width = 8, height = 6, dpi=500)

df %>%
  ggplot(aes(Date, PN)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationId, ncol=2) +
      labs(title = "", x = "", y = "Part N") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/OKOKYST_Klima/PN_pr_station.png", width = 8, height = 6, dpi=500)

df %>%
  ggplot(aes(Date, PP)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationId, ncol=2) +
      labs(title = "", x = "", y = "Part P ") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/OKOKYST_Klima/PP_pr_station.png", width = 8, height = 6, dpi=500)


df %>%
  subset(Date >= "2021-01-01" &  Date <= "2021-12-31") %>%
  ggplot(aes(Date,a_443 )) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationId, ncol=2) +
      labs(title = "", x = "", y = "Part P ") +
        scale_x_date(date_breaks = "1 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/cDOM_pr_station.png", width = 8, height = 6, dpi=500)

df %>%
  subset(Date >= "2021-01-01" &  Date <= "2021-12-31") %>%
  filter(StationId!="VT3")%>%
  ggplot(aes(Date,a_443 )) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationId, ncol=2) +
      labs(title = "", x = "", y = "cdom absorption/m ") +
        scale_x_date(date_breaks = "1 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/cDOM_pr_station.png", width = 8, height = 6, dpi=500)


```

### Property plots
```{r}
# DOC vs salt
df %>%
  ggplot(aes(Salinitet, DOC)) + 
    geom_point() +
    facet_wrap(~StationId, ncol=2)

# DOC vs cDOM
df %>%
  filter(DOC > 0 & a_443 > 0)%>%
    filter(DOC < 3) %>%
  ggplot(aes(DOC, a_443)) + 
    geom_point() +
    geom_smooth(method = lm, se = FALSE) + 
    facet_wrap(~Depth1)

ggsave ("Figures/DOC_cdom_.png", width = 8, height = 6, dpi=500)


df %>%
  filter(StationId=="VR21") %>%
  filter(DOC > 0 & a_443 > 0)%>%
  ggplot(aes(DOC, a_443)) + 
    geom_point() +
    geom_smooth(method = lm, se = FALSE) + 
    facet_wrap(vars(Depth1))

ggsave ("Figures/DOC_cdom_VR21.png", width = 8, height = 6, dpi=500)

         
  mod1<-  lm(DOC~a_443, df)
summary(mod1)



df %>%
  filter(StationId=="VR54") %>%
  filter(DOC > 0 & a_443 > 0)%>%
   # filter(DOC < 3) %>%
  ggplot(aes(DOC, a_443)) + 
    geom_point() +
    geom_smooth(method = lm, se = FALSE)+ 
    facet_wrap(~Depth1)

ggsave ("Figures/DOC_cdom_VR54_wrap.png", width = 8, height = 6, dpi=500)

# cdom vs salt
df %>%
  ggplot(aes(Salinitet, a_443)) + 
    geom_point() +
    facet_wrap(~StationId, ncol=2)

```

### Station with depth color coded
```{r}
gg_VT4 <- df %>%
  filter(StationId == "VR54") %>%
  #gather("Variable", Value,  Temperature:DIN) %>%

df %>%  
ggplot(aes(Date, DOC)) + 
    ylim (0,5) +
    geom_point() +
      labs(title = "VR54", x = "", y = "DOC (mg/L)") + 
     scale_x_date(date_breaks = "4 month", limits = c(min, max)) +
      theme (axis.text.x=element_blank(),axis.title.x=element_blank(), axis.ticks.length=unit(.25, "cm"), plot.title = element_text(hjust=0.5))

```




### b. Plots pr variable
```{r}

#, scales = "free_y"

# default date axis
df %>%
  ggplot(aes(Date, DOC)) + 
    geom_point() + geom_line() +
    facet_wrap(~StationCode, ncol=2)

df %>%
  ggplot(aes(Month, DOC)) + 
    geom_point() + geom_line() +
    facet_wrap(~StationCode, ncol=2)

#ggsave ("Figurer/DOC_FBstations.png", width = 8, height = 6, dpi=500)

# plot vars with label every 4nd months

df %>%
  ggplot(aes(Date, Sal_FB)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "Salinity") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/Sal_FBstations_smooth.png", width = 8, height = 6, dpi=500)

df %>%
  ggplot(aes(Date, Temp_FB)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "Temperature (C)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/Temp_FBstations_smooth.png", width = 8, height = 6, dpi=500)

range (df$Date)

df %>%
  ggplot(aes(Date, DOC)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "DOC (mg/L)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/DOC_FBstations_smooth.png", width = 8, height = 6, dpi=500)

df %>%
  ggplot(aes(Date, DOC)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "DOC (mg/L)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/DOC_FBstations_smooth.png", width = 8, height = 6, dpi=500)

# plot Chla
df %>%
  ggplot(aes(Date, KlfA)) + 
    geom_point() + geom_line() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "Chla (ug/l)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y") +
        theme(axis.text.x=element_text(angle=60, hjust=1))

#ggsave ("Figures/Chla_FBstations.png", width = 8, height = 6, dpi=500)

# plot No3+NO2
df %>%
  ggplot(aes(Date, NO3)) + 
    geom_point() + geom_line() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "NO3 (ug/l)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y") +
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/NO3_FBstations.png", width = 8, height = 6, dpi=500)

# plot NH4
df %>%
  ggplot(aes(Date, NH4)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "NH4 (ug/l)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y") +
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/NH4_FBstations_smooth.png", width = 8, height = 6, dpi=500)

# plot PO4
df %>%
  ggplot(aes(Date, PO4)) + 
    geom_point() + geom_line() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "PO4 (ug/l)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y") +
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/PO4_FBstations_V2.png", width = 8, height = 6, dpi=500)

# plot TotN
df %>%
  ggplot(aes(Date, TOTN)) + 
    geom_point() + geom_line() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "TOTN (ug/l)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y") +
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/TOTN_FBstations_V2.png", width = 8, height = 6, dpi=500)

# plot TotP
df %>%
  ggplot(aes(Date, TOTP)) + 
    geom_point() + geom_line() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "TOTP (ug/l)") +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y") +
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/TOTP_FBstations_V2.png", width = 8, height = 6, dpi=500)

# plot cdom
df %>%
  subset(Date >= "2021-01-01" &  Date <= "2021-12-31") %>%
  ggplot(aes(Date, a_443, Fill=)) + 
    geom_point() +
    facet_wrap(~StationId, ncol=2) +
      labs(title = "", x = "", y = "cDOM (ug/l)") +
        scale_x_date(date_breaks = "1 month", date_labels =  "%m-%y") +
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/cDOM_pr_station.png", width = 8, height = 6, dpi=500)

```


### c. Plots pr FB station

```{r}
#str(df)
#levels (df$StationCode)
#"VT4"  "VT12" "VT72" "VT23" "VT45" "VT22" "VT80" "VR25" "VR23" "VT76"
# for OKOKYST; "VT3"  "VT16" "VT71" "VR54" "VR58" "VR21" 

df %>%
      subset(Date >= "2021-01-01" &  Date <= "2021-12-31") %>%
  select(-O2_mg, -O2_ml, -NO3_NO2, -NH4, -PO4,-SiO2,  -TOTN, -TOTP)%>%
  gather("Var", "Concentration",  Salinitet:Slope) %>%
  mutate(Var=factor(Var, levels = c("Salinitet","Temperatur","Turbiditet", "Siktdyp", "DOC", "KlfA",   "POC", "PN", "PP", "TSM","a_443", "Slope")))  %>%
  filter(StationId == "VT16") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VT16")

ggsave("Figures/VT16_allvars.png")

df %>%
  gather("Var", "Concentration", DOC:TOTN) %>%
  mutate(Var=factor(Var, levels = c( "Sal_FB","Temp_FB", "DOC", "KlfA", "NO3", "PO4", "NH4", "SiO2", "TOTN", "TOTP")))  %>%
  filter(StationId == "VT12") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VT12")

ggsave("Figures/VT12_allvars.png")


df %>%
  gather("Var", "Concentration", DOC:TOTN) %>%
  mutate(Var=factor(Var, levels = c( "Sal_FB","Temp_FB", "DOC", "KlfA", "NO3", "PO4", "NH4", "SiO2", "TOTN", "TOTP")))  %>%
  filter(StationId == "VT72") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VT72")

ggsave("Figures/VT72_allvars.png")

df %>%
  gather("Var", "Concentration", DOC:TOTN) %>%
  mutate(Var=factor(Var, levels = c( "Sal_FB","Temp_FB", "DOC", "KlfA", "NO3", "PO4", "NH4", "SiO2", "TOTN", "TOTP")))  %>%
  filter(StationId == "VT23") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VT23")

ggsave("Figures/VT23_allvars.png")

df %>%
  gather("Var", "Concentration", DOC:TOTN) %>%
  mutate(Var=factor(Var, levels = c( "Sal_FB","Temp_FB", "DOC", "KlfA", "NO3", "PO4", "NH4", "SiO2", "TOTN", "TOTP")))  %>%
  filter(StationId == "VT80") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VT80")

ggsave("Figures/VT80_allvars.png")

df %>%
  gather("Var", "Concentration", DOC:TOTN) %>%
  mutate(Var=factor(Var, levels = c( "Sal_FB","Temp_FB", "DOC", "KlfA", "NO3", "PO4", "NH4", "SiO2", "TOTN", "TOTP")))  %>%
  filter(StationId == "VT22") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VT22")

ggsave("Figures/VT22_allvars.png")

df %>%
  gather("Var", "Concentration", DOC:TOTN) %>%
  mutate(Var=factor(Var, levels = c( "Sal_FB","Temp_FB", "DOC", "KlfA", "NO3", "PO4", "NH4", "SiO2", "TOTN", "TOTP")))  %>%
  filter(StationId == "VT45") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VT45")

ggsave("Figures/VT45_allvars.png")

df %>%
  gather("Var", "Concentration", Salinitet:Slope) %>%
  mutate(Var=factor(Var, levels = c( "Sal_FB","Temp_FB", "DOC", "KlfA", "NO3", "PO4", "NH4", "SiO2", "TOTN", "TOTP")))  %>%
  filter(StationId == "VR25") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VR25")

ggsave("Figures/VR25_allvars.png")

df %>%
  gather("Var", "Concentration", DOC:TOTN) %>%
  mutate(Var=factor(Var, levels = c( "Sal_FB","Temp_FB", "DOC", "KlfA", "NO3", "PO4", "NH4", "SiO2", "TOTN", "TOTP")))  %>%
  filter(StationId == "VR23") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VR23")

ggsave("Figures/VR23_allvars.png")

df %>%
  gather("Var", "Concentration", DOC:TOTN) %>%
  mutate(Var=factor(Var, levels = c( "Sal_FB","Temp_FB", "DOC", "KlfA", "NO3", "PO4", "NH4", "SiO2", "TOTN", "TOTP")))  %>%
  filter(StationId == "VT76") %>%
  ggplot(aes(Date, Concentration)) +
    geom_smooth() +
    geom_point() +
    facet_wrap(~Var, scales = "free_y", ncol = 2)+
    ggtitle("VT76")

ggsave("Figures/VT76_allvars.png")


```

### d. DOC timeser with COVID shutdown of Trollfjord
```{r}
df %>%
  ggplot(aes(Date, DOC)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationCode, ncol=2) +
      labs(title = "", x = "", y = "DOC (mg/L)") +
      geom_vline(xintercept = as.numeric(ymd("2020-03-14")), linetype="dashed", 
                color = "red", size=1) +
        scale_x_date(date_breaks = "4 month", date_labels =  "%m-%y")+
        theme(axis.text.x=element_text(angle=60, hjust=1))

ggsave ("Figures/DOC_FBstations_COVID.png", width = 8, height = 6, dpi=500)
```

### e. Monthly climatologies
```{r}
str(df)
df_m <- df %>%
  group_by(Month, StationCode) %>%
  summarize_at(vars(DOC:TOTN), mean, na.rm = TRUE)

str(df_m)

df_m %>%
  ggplot(aes(Month, DOC)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationCode, ncol=2)

ggsave ("Figures/DOC_FBstations_monthly.png", width = 8, height = 6, dpi=500)

df_m %>%
  ggplot(aes(Month, NH4)) + 
    geom_point() + geom_smooth() +
    facet_wrap(~StationCode, ncol=2)

ggsave ("Figures/NH4_FBstations_monthly.png", width = 8, height = 6, dpi=500)

```


### f. Property-property plots
```{r}

range (df$Date)

# DOC vs salt
df %>%
  ggplot(aes(Salinitet, DOC)) + 
    geom_point() +
    facet_wrap(~StationId, ncol=5)

ggsave("Figures/DOCvsSal.png")

df %>%
  ggplot(aes(NH4, DOC)) + 
    geom_point() +
    facet_wrap(~StationCode, ncol=5)

ggsave("Figures/DOCvsNH4.png")

df %>%
  ggplot(aes(NH4, KlfA)) + 
    geom_point() +
    facet_wrap(~StationCode, ncol=5)

ggsave("Figures/DOCvsKlfA.png")

str (df)


## vs more variables, for one station at a time
# rename variables for facet labels
new_labels <- c("a_443" = "cDOM", "KlfA" =  "Chl a (ug/l)", "NH4" =  "NH4 (ug/l)")

#"VT4"  "VT12" "VT72" "VT23" "VT45" "VT22" "VT80" "VR25" "VR23" "VT76"

df %>%
  filter(StationId == "VT12") %>%
  gather(key = "var", value = "value", a_443, KlfA, NH4) %>%
  mutate(var=factor(var, levels = c("a_443", "NH4", "KlfA")))  %>%
  ggplot(aes(x = value, y = a_443)) + 
    #ylim (0,3.8) +
    geom_point() +
      facet_wrap(~ var, scales = "free", labeller = labeller(var = new_labels), ncol = 1) +
        labs(title = "VT12", y = "DOC (mg/L)") + 
          theme (plot.title = element_text(hjust=0.5))

ggsave("Figures/VT12_vs.png")

```
### x. code for combining water column station and FB station, for later if include ØKOKYST klima water colums stations...
```{r}

# Skagerrak: VT4 (Hvitsten) + VT3 Torbj?rnskj?r

gg_VT4 <- df %>%
  filter(StationCode == "VT4") %>%
  #gather("Variable", Value,  Temperature:DIN) %>%
  ggplot(aes(Date, DOC)) + 
    ylim (0,3.8) +
    geom_point() + geom_line() +
      labs(title = "VT4:Hvitsten", x = "", y = "DOC (mg/L)") + 
     scale_x_date(date_breaks = "1 month", limits = c(min, max)) +
      theme (axis.text.x=element_blank(),axis.title.x=element_blank(), axis.ticks.length=unit(.25, "cm"), plot.title = element_text(hjust=0.5))
gg_VT4

gg_VT3 <- df_discrete %>%
  filter(StationId == "VT3" & Depth == 5) %>%
  #gather("Variable", Value,  Temperature:DIN) %>%
  ggplot(aes(Date, DOC)) + 
    ylim (0,3.8) +
    geom_point() + geom_line() +
      labs(title = "VT3:Torbj?rnskj?r", x = "", y = "DOC (mg/L)") + 
     scale_x_date(date_breaks = "1 month", limits = c(min, max))+
          theme (axis.text.x=element_text(angle=90, hjust=1), axis.ticks.length=unit(.25, "cm"),  
                plot.title = element_text(hjust=0.5))
gg_VT3

# combine figures (with patchwork library)
Skag <- gg_VT4 / gg_VT3

plot (Skag)
#ggsave("Figurer/Skagerrak_DOC.png", plot = Skag)

```

### z. VT3
```{r}

str (df_discrete)

# POC ?g/l C

df_discrete$POC_mg <- df_discrete$POC / 1000

# rename variables for facet labels
new_labels_2 <- c("Salinitet" = "Salinitet", "KlfA" =  "Chl a (?g/l)", "POC_mg" = "POC (mg/L)")


# kun 5 m
gg_VT3_vs_5m <- df_discrete %>%
  filter(StationId == "VT3" & Depth == 5) %>%
  gather(key = "var", value = "value", Salinitet, KlfA, POC_mg) %>%
  mutate(var=factor(var, levels = c("Salinitet", "KlfA", "POC_mg")))  %>%
  ggplot(aes(x = value, y = DOC)) + 
    #ylim (0,3.8) +
    geom_point() +
      facet_wrap(~ var, scales = "free", labeller = labeller(var = new_labels_2)) +
        labs(title = "VT3:Torbj?rnskj?r - 5m", y = "DOC (mg/L)") + 
          theme (plot.title = element_text(hjust=0.5))
gg_VT3_vs_5m

ggsave("Figurer/Skagerrak_VT3_vs_5m.png", plot = gg_VT3_vs_5m)


# med ulike dyp
gg_VT3_vs_depth <- df_discrete %>%
  filter(StationId == "VT3") %>%
  gather(key = "var", value = "value", Salinitet, KlfA, POC_mg) %>%
  mutate(var=factor(var, levels = c("Salinitet", "KlfA", "POC_mg")))  %>%
  ggplot(aes(x = value, y = DOC)) + 
    #ylim (0,3.8) +
    geom_point() +
      facet_grid(Depth ~ var, scales = "free_x", labeller = labeller(var = new_labels_2)) +
        labs(title = "VT3:Torbj?rnskj?r", y = "DOC (mg/L)") + 
          theme (plot.title = element_text(hjust=0.5))
gg_VT3_vs_depth

ggsave("Figurer/Skagerrak_VT3_vs_alldepth.png", plot = gg_VT3_vs_depth)

```
test