---
title: "03. Plotting_discrete_stations"
author: "Helene"
date: "14 april 2021"
output: github_document:
    toc: true
  html_document:
    toc: true    
    toc_float: true
    code_folding: hide
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_format = "all", output_dir = "../Produced_documents") })

---

* NB uses datsets for Vt3, VR54 and VR24 that is made in Vaarflom_check_data_aquamonitor. Datasets are averaged for discrete depths between 0-30 m (ie. df1_m etc).

## 0. Libraries
```{r, error = F, warning = F}

# clean workspace
#rm(list=ls())

library (caTools)
library (lubridate)
library (dplyr)
#install.packages ("vctrs")
#install.packages ("ellipsis")
library (vctrs)
library (ellipsis)
library(tidyr)     # 
library(purrr)     # for map_dbl
#install.packages ("rMR")
library (rMR) # calculate O2 saturation
library (seacarb)
library(akima)
library(ggplot2)
library(readxl)
library(mgcv)     # for gam() in plots
library(patchwork) # for arranging plots in panels

# specific functions needed for the contour plots

# Functions (okokyst_plot and others)
#source("12_Plotting_discrete_stations_functions.R") # old version from 2020

# NB! this R script file contains the function (that is called in this script), and needs to be saved in the same folder
source("okokyst_plot_functions.R")# new version in 2021

# Use a self-defined color scale  
jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", 
                                 "yellow", "#FF7F00", "red", "#7F0000"))

```


## 1. Read and clean files
### a. read
* this file is produced in script "Read_and_check_OKOKYST_Klima.Rmd"
```{r}

# clear workspace
#rm(list = ls())
#dir("Datasett")

df <- read.delim ("Datasett/OKOKYST_Klima_cleaned_merged.txt")

str(df)

# convert back to Date
df$Date <- as.Date(df$Date)
#str(df)

# station naming
df$StationId <- as.factor (df$StationId)
#order stations along coastline for ggplot
df$StationId <- factor(df$StationId, levels = c("VT3", "VT16", "VT71", "VR54", "VR58", "VR21"))



```

### 1. Clean data for contour plots, summarizing for depths
```{r}

str (df)
# For water chemistry variables with discrete depths (0-30m)  
df_chem <- df %>%
  select(-c(Depth2:Turbiditet, O2_mg, O2_ml))  %>%
   filter (Depth1 == 0.0 | Depth1 == 5.0 | Depth1 == 10.0 | Depth1 == 20.0 | Depth1 == 30.0) %>%
   rename (Depth = Depth1)

#str(df_chem)

df_chem_m <- df_chem %>%
group_by(StationId, Date, Depth) %>%
  summarize_at(vars(DOC:TSM), mean, na.rm = TRUE) %>%
    ungroup ()

# (df_chem_m)

# make df for each station (needed for okokyst_plot function)

#include only data from 2017 to 2021 (or just 2020?)
#range (df$Date)
#df <- subset(df, Date >= "2017-01-01" &  Date <= "2021-12-31")

VT16 <- df_chem_m %>%
  filter(StationId == "VT16") %>%
  filter (Date >= "2021-06-01" &  Date <= "2021-11-30" )

VT71 <- df_chem_m %>%
  filter(StationId == "VT71")

VR54 <- df_chem_m %>%
  filter(StationId == "VR54")

VR58 <- df_chem_m %>%
  filter(StationId == "VR58") %>%
  filter (Date >= "2021-06-01" &  Date <= "2021-11-30" )

VR21 <- df_chem_m %>%
  filter(StationId == "VR21") %>%
  filter (Date >= "2021-06-01" &  Date <= "2021-11-30" )

```

### 3. Contour plots

### o. example from Dag 13.04.2021 - just for testing
```{r}
## Using okokyst_plot() function ---- 
#str(df2)

# Basic plot
# debugonce(okokyst_plot)
okokyst_plot(VR54, "DOC")

# Don't show the coloured points (can instead use 'colored_points_size' to adjust size)
okokyst_plot(df2, "KlfA", colored_points = FALSE)

# If you want to remove part of the background colors, then
# (1) first use okokyst_make_plotdata()  (here, we call the result 'my_plotdata')
# (2) select the part of the data and store the result (here, called 'sel')
# (3) set the variable 'z' in the dataset from 1 ('my_plotdata') to be NA for all selected rows ('sel')
# (4) use okokyst_plot() as before, but set plotdata = the name of the dataset from 1 (here, 'my_plotdata') 
# Example:
my_plotdata <- okokyst_make_plotdata(df2, "KlfA")  
sel <- with(my_plotdata, Time >= dmy("01.05.2020") & Time <= dmy("31.05.2020") & Depth < 15)
my_plotdata$z[sel] <- NA
okokyst_plot(df2, "KlfA", plotdata = my_plotdata)

# Try GAM (doesn't work well in this case)
okokyst_plot(df1_discrete, "KlfA", gam = TRUE, gam_k = 5)

# Try a different palette (you can set palette = 'A', 'B', 'C' or 'D' - the default is D)
okokyst_plot(df1_discrete, "KlfA", palette = "C")

# Turn colors "upside down" (setting colored_points_rim = TRUE to see points in all parts)
okokyst_plot(df1_discrete, "KlfA", palette = "A", 
             reverse_colors = TRUE, colored_points_rim = TRUE)

okokyst_plot(df2, "KlfA") +
  scale_fill_gradientn(colours = jet.colors(16))

```




### a. VR21 (will make panels for all climate vars pr station)

#### DOC
```{r}

quantile (VR21$DOC, na.rm = T)

# med punkter - uten x akse (til panels)
VR21_DOC <- okokyst_plot(data = VR21, varname = "DOC", ctd_variable = FALSE,
                   colored_points = TRUE, gam = T, gam_k = 5, limits = c(0, 1.9), binwidth = 0.2, max_timediff = 30, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("DOC", colours = jet.colors(16)) +
                    scale_x_datetime(date_breaks = "1 month", labels =  NULL)
VR21_DOC

ggsave ("Figures/VR21_DOC.png", dpi=500)
```

#### cDOM (do not have yet...)
```{r}

quantile (VR21$cDOM, na.rm = T)

# med punkter - uten x akse (til panels)
VR21_DOC <- okokyst_plot(data = VR21, varname = "DOC", ctd_variable = FALSE,
                   colored_points = TRUE, gam = T, gam_k = 5, limits = c(0, 1.9), binwidth = 0.2, max_timediff = 30, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("DOC", colours = jet.colors(16)) +
                    scale_x_datetime(date_breaks = "1 month", labels =  NULL)
VR21_DOC

ggsave ("Figures/VR21_cDOM.png", dpi=500)
```

#### TSM
```{r}

quantile (VR21$TSM, na.rm = T)

# med punkter - uten x akse (til panels)
VR21_TSM <- okokyst_plot(data = VR21, varname = "TSM", ctd_variable = FALSE,
                   colored_points = TRUE, gam = T, gam_k = 5, limits = c(0, 1.2), binwidth = 0.2, max_timediff = 30, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TSM", colours = jet.colors(16)) +
                    scale_x_datetime(date_breaks = "1 month", date_labels =  "%b %y") +
                    theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR21_TSM

ggsave ("Figures/VR21_TSM.png", dpi=500)
```

#### POC
```{r}

quantile (VR21$POC, na.rm = T)

# med punkter - uten x akse (til panels)
VR21_POC <- okokyst_plot(data = VR21, varname = "POC", ctd_variable = FALSE,
                   colored_points = TRUE, gam = T, gam_k = 4, limits = c(0, 280), binwidth = 50, max_timediff = 30, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("POC", colours = jet.colors(16)) +
                    scale_x_datetime(date_breaks = "1 month", labels =  NULL)
VR21_POC

ggsave ("Figures/VR21_POC.png", dpi=500)
```

#### PN - sjekk verdier...
```{r}

quantile (VR21$PN, na.rm = T)

# med punkter - uten x akse (til panels)
VR21_PN <- okokyst_plot(data = VR21, varname = "PN", ctd_variable = FALSE,
                   colored_points = TRUE, gam = T, gam_k = 4, limits = c(0, 43), binwidth = 5, max_timediff = 1, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("PN", colours = jet.colors(16)) +
                    scale_x_datetime(date_breaks = "1 month", labels =  NULL)
VR21_PN

ggsave ("Figures/VR21_PN.png", dpi=500)
```

#### PP
```{r}

quantile (VR21$PP, na.rm = T)

# med punkter - uten x akse (til panels)
VR21_PP <- okokyst_plot(data = VR21, varname = "PP", ctd_variable = FALSE,
                   colored_points = TRUE, gam = T, gam_k = 5, limits = c(0,9), binwidth = 1, max_timediff = 30, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("PP", colours = jet.colors(16)) + 
                    scale_x_datetime(date_breaks = "1 month", date_labels =  "%b %y") +
                    theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR21_PP

ggsave ("Figures/VR21_PP.png", dpi=500)
```


### Combine figures (with patchwork library)
```{r}

# combine figures pr station 

# NB!! also add cDOm in the middle of this panel
P1 <- VR21_DOC +  VR21_TSM + plot_layout(ncol = 1)
plot (P1)
ggsave("Figures/VR21_panel_1.png", plot = P1)

P2 <- VR21_POC + VR21_PN + VR21_PP + plot_layout(ncol = 1)
plot (P2)
ggsave("Figures/VR21_panel_2.png", plot = P2)

```


### VR54

#### DOC
```{r}

quantile(VR54$DOC, na.rm = T)

# med punkter
VR54_DOC <- okokyst_plot(data = VR54, varname = "DOC", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 4.8), binwidth = 1, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("DOC", colours = jet.colors(16))  +
                    scale_x_datetime(date_breaks = "2 month", labels =  NULL)
VR54_DOC

ggsave ("Figures/VR54_DOC.png", dpi=500)


```

####cDOM (NB! do not have yet)
```{r}

quantile(VR54$cDOM, na.rm = T)

# med punkter
VR54_cDOM <- okokyst_plot(data = VR54, varname = "cDOM", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 4.8), binwidth = 1, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("cDOM", colours = jet.colors(16))  +
                    scale_x_datetime(date_breaks = "2 month", labels =  NULL)
VR54_DOC

ggsave ("Figures/VR54_cDOM.png", dpi=500)


```

#### TSM
```{r}

quantile (VR54$TSM, na.rm = T)

# med punkter - med x aksen
VR54_TSM <- okokyst_plot(data = VR54, varname = "TSM", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0,3), binwidth = 0.5, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("TSM", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
                    theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR54_TSM

ggsave ("Figures/VR54_TSM.png", dpi=500)

```

#### POC - NB sjekk verdier, kanskje bare bruke siden Juni 2021???
```{r}

quantile (VR54$POC, na.rm = T)

# med punkter - uten x akse (til panels)
VR54_POC <- okokyst_plot(data = VR54, varname = "POC", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 410), binwidth = 50, max_timediff = 30, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("POC", colours = jet.colors(16)) +
                    scale_x_datetime(date_breaks = "1 month", labels =  NULL)
VR54_POC

ggsave ("Figures/VR54_POC.png", dpi=500)
```

#### PN - sjekk verdier...
```{r}

quantile (VR54$PN, na.rm = T)

# med punkter - uten x akse (til panels)
VR54_PN <- okokyst_plot(data = VR54, varname = "PN", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 273), binwidth = 50, max_timediff = 1, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("PN", colours = jet.colors(16)) +
                    scale_x_datetime(date_breaks = "1 month", labels =  NULL)
VR54_PN

ggsave ("Figures/VR54_PN.png", dpi=500)
```

#### PP
```{r}

quantile (VR54$PP, na.rm = T)

# med punkter - uten x akse (til panels)
VR54_PP <- okokyst_plot(data = VR54, varname = "PP", ctd_variable = FALSE,
                   colored_points = TRUE, gam = T, gam_k = 5, limits = c(0,26), binwidth = 5, max_timediff = 30, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("PP", colours = jet.colors(16)) + 
                    scale_x_datetime(date_breaks = "1 month", date_labels =  "%b %y") +
                    theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR54_PP

ggsave ("Figures/VR54_PP.png", dpi=500)
```


### Combine figures (with patchwork library)
```{r}

# combine figures pr station 

# NB!! also add cDOm in the middle of this panel
P1 <- VR54_DOC +  VR54_TSM + plot_layout(ncol = 1)
plot (P1)
ggsave("Figures/VR54_panel_1.png", plot = P1)

# need to change timescale - just use from Jun2021?
P2 <- VR54_POC + VR54_PN + VR54_PP + plot_layout(ncol = 1)
plot (P2)
ggsave("Figures/VR21_panel_2.png", plot = P2)

```


# NOT UPDATED - DO NOT USE!

#### VT71
```{r}

quantile (VT71$DOC, na.rm = T)

# med punkter - uten x akse (til panels)
VT71_DOC <- okokyst_plot(data = VT71, varname = "DOC", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 3.2), binwidth = 0.5, max_timediff = 25, ylabel = F, xlabel = F) +
                    scale_fill_gradientn("DOC", colours = jet.colors(16)) +
                    scale_x_datetime(date_breaks = "2 month", labels =  NULL)
VT71_DOC

ggsave ("Figurer/VT71_DOC.png", dpi=500)
```


### e. TSM

#### VT71
```{r}



quantile(VT71$TSM, na.rm = T)

# med punkter
VT71_TSM <- okokyst_plot(data = VT71, varname = "TSM", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 2), binwidth = 2, max_timediff = 25, ylabel = F) +
                    scale_fill_gradientn("TSM", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
  theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VT71_TSM

ggsave ("Figures/VT71_TSM.png", dpi=500)


```
#### VR54
```{r}

quantile(df2_m$TSM, na.rm = T)

# med punkter
VR54_TSM <- okokyst_plot(data = df2_m, varname = "TSM", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 3), binwidth = 1) +
                    scale_fill_gradientn("TSM", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
  theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR54_TSM

ggsave ("Figurer/VR54_TSM.png", dpi=500)


```
#### VR24
```{r}

quantile(df3_m$TSM, na.rm = T)

# med punkter
VR24_TSM <- okokyst_plot(data = df3_m, varname = "TSM", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 1.2), binwidth = 0.5) +
                    scale_fill_gradientn("TSM", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
  theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR24_TSM

ggsave ("Figurer/VR24_TSM.png", dpi=500)


```
### f. SiO2

#### VT3
```{r}

quantile(df1_m$SiO2, na.rm = T)

# med punkter
VT3_Si <- okokyst_plot(data = df1_m, varname = "SiO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 2), binwidth = 2, max_timediff = 25, ylabel = F) +
                    scale_fill_gradientn("SiO2", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
  theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VT3_Si

ggsave ("Figurer/VT3_Si.png", dpi=500)


```
#### VR54
```{r}

quantile(df2_m$SiO2, na.rm = T)

# med punkter
VR54_Si <- okokyst_plot(data = df2_m, varname = "SiO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 2), binwidth = 1) +
                    scale_fill_gradientn("SiO2", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
  theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR54_Si

ggsave ("Figurer/VR54_Si.png", dpi=500)


```
#### VR24
```{r}

quantile(df3_m$SiO2, na.rm = T)

# med punkter
VR24_Si <- okokyst_plot(data = df3_m, varname = "SiO2", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 1), binwidth = 50) +
                    scale_fill_gradientn("SiO2", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
  theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR24_Si

ggsave ("Figurer/VR24_Si.png", dpi=500)


```

### g. NH4

#### VT3
```{r}

quantile(df1_m$NH4, na.rm = T)

# med punkter
VT3_NH4 <- okokyst_plot(data = df1_m, varname = "NH4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 67), binwidth = 10, max_timediff = 25, ylabel = F) +
                    scale_fill_gradientn("NH4", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
  theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VT3_NH4

ggsave ("Figurer/VT3_NH4.png", dpi=500)


```
#### VR54
```{r}

quantile(df2_m$NH4, na.rm = T)

# med punkter
VR54_NH4 <- okokyst_plot(data = df2_m, varname = "NH4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 78), binwidth = 10, max_timediff = 25, ylabel = F) +
                    scale_fill_gradientn("NH4", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
  theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR54_NH4

ggsave ("Figurer/VR54_NH4.png", dpi=500)


```
#### VR24
```{r}

quantile(df3_m$NH4, na.rm = T)

# med punkter
VR24_NH4 <- okokyst_plot(data = df3_m, varname = "NH4", ctd_variable = FALSE,
                   colored_points = TRUE, limits = c(0, 81), binwidth = 10, max_timediff = 25, ylabel = F) +
                    scale_fill_gradientn("NH4", colours = jet.colors(16)) +
                     scale_x_datetime(date_breaks = "2 month", date_labels =  "%b %y") +
  theme(axis.text.x=element_text(angle=60, hjust=1), plot.title = element_text(hjust = 0.5))
VR24_NH4

ggsave ("Figurer/VR24_NH4.png", dpi=500)


```

### Combine figures (with patchwork library)
```{r}
# combine figures 
VT3 <- VT3_NO3 +  VT3_DOC + VT3_KlfA + VT3_TSM + plot_layout(ncol = 1)
plot (VT3)
ggsave("Figurer/VT3_panel_chem.png", plot = VT3)

VR54 <- VR54_NO3 + VR54_DOC + VR54_Chla + VR54_TSM + plot_layout(ncol = 1)
plot (VR54)
ggsave("Figurer/VR54_panel_chem.png", plot = VR54)

VR24 <- VR24_NO3 + VR24_Chla + VR24_TSM + plot_layout(ncol = 1)
plot (VR24)
ggsave("Figurer/VR24_panel_chem.png", plot = VR24)
  
```



### Making plots of depth profiles
```{r}
library(reshape2)

str (df_plot)
df_sel <- select (df_plot, Date, Depth, Temp, Salt, CT, AT, pH_T, O_Ar)
  
  
df_melt <-
  df_sel %>%
  melt(id.vars = c("Depth", "Date"))

profile_2019 <- df_melt %>%
  filter (Date < as.Date ("2020-01-25")) %>%
  ggplot(aes(y = Depth, x = value, color = as.factor (Date))) +
  geom_path() +
  facet_wrap(~variable
             , ncol = 2
             , scales = "free_x") +
  scale_y_reverse() +
  labs(x="Value", y="Depth (m)", color="Date") +
  theme_bw()
profile_2019

profile_2020 <- df_melt %>%
  filter (Date >= as.Date ("2020-01-25")) %>%
  ggplot(aes(y = Depth, x = value, color = as.factor (Date))) +
  geom_path() +
  facet_wrap(~variable
             , ncol = 2
             , scales = "free_x") +
  scale_y_reverse() +
  labs(x="Value", y="Depth (m)", color="Date") +
  theme_bw()
profile_2020

ggsave ("Figurer/2020 data/VR54_Profiles_2020.png", dpi=500)

```


### Making plots of depth profiles
```{r}
library(reshape2)

str (df_plot2)
# for variables to incl in report
df_sel <- select (df_plot2, Date, Depth, Temp, Salt,  pH_T, O_Ar)
  
df_melt <-
  df_sel %>%
  melt(id.vars = c("Depth", "Date"))

# both 2019 and 2020
profile_1 <- df_melt %>%
  ggplot(aes(y = Depth, x = value, color = as.factor (Date))) +
  geom_path() +
  facet_wrap(~variable
             , ncol = 2
             , scales = "free_x") +
  scale_y_reverse() +
  labs(x="Value", y="Depth (m)", color="Date") +
  theme_bw()
profile_1

str

profile_2020_rapp <- df_melt %>%
  filter (Date >= as.Date ("2020-01-25")& Variable == "Temp") %>%
  ggplot(aes(y = Depth, x = value, color = as.factor (Date))) +
  geom_path() +
  geom_point () +
  facet_wrap(~variable
             , ncol = 2
             , scales = "free_x") +
  scale_y_reverse() +
  labs(x="Value", y="Depth (m)", color="Date") +
  theme_bw()
profile_2020


# CT AT for appendix
df_sel_1 <- select (df_plot2, Date, Depth, CT, AT)
  
df_melt_1 <-
  df_sel_1 %>%
  melt(id.vars = c("Depth", "Date"))

profile_2020_1 <- df_melt_1 %>%
  filter (Date >= as.Date ("2020-01-25")) %>%
  ggplot(aes(y = Depth, x = value, color = as.factor (Date))) +
  geom_path() +
  geom_point () +
  facet_wrap(~variable
             , ncol = 2
             , scales = "free_x") +
  scale_y_reverse() +
  labs(x="Value", y="Depth (m)", color="Date") +
  theme_bw()
profile_2020_1

ggsave ("Figurer/2020 data/SVR1_Profiles_CT_AT.png", dpi=500)


# nutrients for appendix
df_sel_2 <- select (df_plot2, Date, Depth, NO3_NO2, PO4, SiO2)
  
df_melt_2 <-
  df_sel_2 %>%
  melt(id.vars = c("Depth", "Date"))

profile_2020_2 <- df_melt_2 %>%
  filter (Date >= as.Date ("2020-01-25")) %>%
  ggplot(aes(y = Depth, x = value, color = as.factor (Date))) +
  geom_path() +
  geom_point () +
  facet_wrap(~variable
             , ncol = 3
             , scales = "free_x") +
  scale_y_reverse() +
  labs(x="Value", y="Depth (m)", color="Date") +
  theme_bw()
profile_2020_2

ggsave ("Figurer/2020 data/SVR1_Profiles_nutrients.png", dpi=500)

`